### 2020-12-06 fe_px_paper/Response_to_Reviewers.tex

  \renewcommand*{\thefootnote}{\alph{footnote}}

  \noindent I am writing to submit my point-by-point responses to the issues raised by the reviewers for my submitted manuscript entitled \enquote{\emph{Proton-induced reactions on Fe, Cu, \& Ti from threshold to 55 MeV}},  for publication in European Physical Journal A.  Please find my responses detailed in \colornote{red text.}

  \noindent Along with my co-authors, I wanted to take the opportunity to personally thank you for your continued assistance in helping along the process of our submitted manuscript, and for finding such thorough and conscientious referees for reviewing it.  We would especially like to thank the referees for their thorough reading and critique, which has made it a better paper. Their comments were very constructive and pointed out some valuable improvements.

  \colornote{Lee - should we make any comments about the hostility and unhelpful/incorrect comment from Reviewer 1 here?}

@@

6. In Fig.3, why the trend of one stack is different from other.

7. EoB should be replaced by EOB.

8. What is the meaning of value in bracket in Tables.

\colornote{Uncertainties are listed in the least significant digit (NDS Style), that is, 131.0(85)\,mb  means 131.0 $\pm$ 8.5\,mb. Clarification to this effect has been added to the caption of all tables.}

@@

9. P-8, line 44, ‘The natFe, natCu and natTi(p,x)......’ is not proper writing.

10. Both the numerical values for all investigated reactions should be given in Table and discussed in
details. But author did not discuss details for the reactions in Appendix.

\colornote{We thank your for this important feedback. We have since greatly expanded the language to include discussion of a dozen additional reaction channels of note, as well as their comparison with model calculations and prior data. As the large volume of cross section data we reported here  impacts  many applications,  we have added this new discussion to help show the importance of these results.}

@@

\colornote{We thank you for this very thoughtful suggestion. Running two overlapping stacks to build confidence through consistency was our goal for this, but the assignment of each foil to a stack is not clear, as you point out.  Tables 1--4, containing all of the measured cross section and ratio data, have all had a new row added, clearly designating the foil corresponding to each proton energy.}

The discussion speaks about the natural iron results in some detail, but almost nothing is said about the irradiations of natural copper and titanium. Please expand the discussion to obtain a fair description of all results.

I strongly suggest creating three figures in the main text, one for each of the irradiate materials (i.e. take these out of the annex). They should support the discussion about the results. In principle, a discussion should follow the pattern: short statements about the comparison to earlier work by channel, short statements about the agreement with models by channel; overall agreement to earlier data and to particular models. Of course, a grouped approach can be taken (several channels of a given nature). Separate messages about the data and their agreement with model estimates from the potential use of the results. Usefulness of the results should be either in the introduction or in an outlook at the end. There is also where implications should be highlighted (outlook at the end of the paper).

\colornote{We thank your for this important feedback. We have since greatly expanded the language to include discussion of a dozen additional reaction channels of note, as well as their comparison with model calculations and prior data. Your point that this new data warrants publication was very well-received, and we have added this new discussion to help show the importance of these results.}

### 2020-12-06 fe_px_paper/fe_body_text.tex
Restructing of results section

These results have several notable features.
The 
% various 
\ce{^{nat}Fe}, \ce{^{nat}Cu}, and \ce{^{nat}Ti}(p,x) cross sections measured here are in excellent agreement with 
% the body of measurements in the 
literature,  but have been measured nearly exclusively with the highest precision to date.
While (p,x) reactions below 70\,MeV on these elements are well-characterized overall, measurements of several reaction channels are somewhat sparse in comparison.
Indeed, fewer than four existing measurements have been performed for the \ce{^{nat}Fe}(p,x)\ce{^{48}Cr},\ce{^{52}Fe}, \ce{^{nat}Cu}(p,x)\ce{^{60}Cu},\ce{^{61}Co}, and \ce{^{nat}Ti}(p,x)\ce{^{44}Sc}
% Similarly, the various \ce{^{nat}Nb}(p,x) cross sections measured here are in excellent agreement with literature data, which is far more sparse in the 40--90\,MeV region than for \ce{^{nat}Cu}(p,x) ---  fewer than three existing measurements have been performed for the majority of the 
reactions presented here.
% Indeed,  the \ce{^{nat}Nb}(p,x)\ce{^{83}Sr}, \ce{^{nat}Nb}(p,x)\ce{^{85}Y}, \ce{^{nat}Nb}(p,x)\ce{^{89}Nb}, \ce{^{nat}Nb}(p,x)\ce{^{90}Mo}, \ce{^{nat}Nb}(p,x)\ce{^{91m}Nb}, and \ce{^{nat}Nb}(p,x)\ce{^{98m}Mo} reactions each possess no more than a total of three data points in this energy region.
% Not only do the \ce{^{nat}Nb}(p,x) measurements in this work fill in the sparse data in this energy region, but they have been measured with the highest precision relative to existing literature data.
Additionally, \ce{^{22,24}Na} activity is seen in all foils, consistent with proton activation of the trace  silicon in the Kapton tape used for foil encapsulation, as described in our previous work\,\cite{Voyles2018a}.
No cross sections for \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} are reported due to the significant uncertainty in characterizing the layer of silicone adhesive, but this serves as another example of how the use of silicone-based adhesives may systematically enhance the apparent fluence when using the \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} monitor reactions.
Discussion of notable reaction channels follows here, and 
comparisons  of the
remaining measured cross sections and isomer branching ratios with modeling results and literature data (retrieved from EXFOR\,\cite{Otuka2014272}) are seen in the figures of 
% Appendices 
\ref{sec:fe_xs_figures} and \ref{sec:fe_ibr_figures}.

@@

        \subfigimg[width=0.485\textwidth]{\hspace{4.5cm}b)}{./figures/52mMn.pdf}{50}
         %         \refstepcounter{subfigure}
         \label{fig:temp_52mMn}
   \hspace{-5pt}}%
    \caption{a) Measured \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} cross section, with \ce{^{56}Fe}(p,$\alpha$n)\ce{^{52}Mn}/\ce{^{54}Fe}(p,2pn)\ce{^{52}Mn} reaction channels visibly peaking at approximately \mbox{30 MeV}.   b) Measured \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn} cross section, with the \ce{^{56}Fe}(p,$\alpha$n)\ce{^{52m}Mn}/\ce{^{54}Fe}(p,2pn)\ce{^{52m}Mn} reaction channels visibly peaking at approximately \mbox{30 MeV}.} 
     \label{fig:discussion_52Mn}
\end{figure*}

@@

\subsection{\ce{^{nat}Ti}(p,x)\ce{^{54, 56}}????? cross sections}

In addition to the \ce{^{nat}Fe}(p,x)\ce{^{51,52}Mn} measurements, this experiment has also yielded measurements of  a number of additional  emerging radionuclides with medical applications.
These include the non-standard positron emitters 
\ce{^{44}Sc}\,\cite{Muller2013,Filosofov2010,Qaim2011}
%\,\cite{Qaim2011,Qaim201731,Kolsky1998,mausner1995evaluation}.
\ce{^{55}Co}\,\cite{Thisgaard2011,Zaman1996,Hermanne2000a}
\ce{^{61}Ni}\,\cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}, 
\ce{^{61}Cu}\,\cite{Szelecsenyi2005a,Fukumura2004}
\ce{^{64}Cu}\,\cite{Lewis2003,Bandari2014,mp500671j,Szelecsenyi1993,Aslam2009,Hilgers2003,Szelecsenyi2005,Voyles2017},
% \ce{^{86}Y}\,\cite{Valdovinos2017,Nickles2003,Qaim2008,QaimSyedM2011,Rosch1993,doi:10.1139/v67-193,levkovski1991cross,Johnson2015,Singh2013,Kiselev1974,Kandil2009}, 
% \ce{^{89}Zr}\,\cite{Verel2003,Dijkers2009,Dijkers2010,PhysRevC.38.1624,Omara2009},  
% \ce{^{90}Nb}\,\cite{Busse2002,Radchenko2012},  
% the $\beta^-$-therapy agent  \ce{^{64}Cu},  
and the $\beta^-$-therapeutic agent 
\ce{^{47}Sc}\,\cite{Muller2014,Deilami-nezhad2016}.
% and the Auger-therapy agent \ce{^{82\text{m}}Rb}\,\cite{Kovacs1991,Titarenko2011}. 
Production of these radionuclides offers no major advantages over established pathways, with the generally lower yields and radioisotopic purities failing to justify the convenience of natural targets  via   \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and  \ce{^{nat}Ti}(p,x). 
% The one possible exception to this trend is the non-standard positron emitter \ce{^{57}Ni} ($t_{1/2}=35.60\pm0.06$ h, $\epsilon$=100\% to \ce{^{57}Co}\,\cite{Bhat1998}) --- the \ce{^{57}Ni}/\ce{^{56}Ni} ratio of production rates is approximately 290 at 61.58\,MeV, and varies from 45--75 at the 70--90\,MeV positions.
% This \ce{^{nat}Cu}(p,x) route offers both higher yield and higher radioisotopic purity over the established  \ce{^{nat}Co}(p,3n) pathway, which suffers from approximately fivefold greater  \ce{^{56}Ni} contamination\,\cite{MICHEL1997153,Ditrói2013}.
% The one potential exception to this is the production of \ce{^{58m}Co}, a potent agent for Auger electron-based targeted therapy\,\cite{Thisgaard2011a,Valdovinos2017b,Thisgaard2014a}.
% While ingrowth of the long-lived \ce{^{58g}Co} ($t_{1/2}$ = 70.86(6) d\,\cite{Nesaraja2010}) is unavoidable, minimizing co-production of \ce{^{58g}Co} is necessary to minimize patient dose.
% The \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} pathway shows a clear \enquote{peak} in the \ce{^{58m}Co}/\ce{^{58g}Co} branching ratio for approximately 15--30\,MeV protons, which might have translational implications if Auger electron therapy becomes more clinically prevalent.

@@

We present here a set of measurements of 34 cross sections for the \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and  \ce{^{nat}Ti}(p,x) reactions up to 55\,MeV, as well as  independent measurements of three isomer branching ratios.
Nearly all cross sections have been reported with higher precision than previous measurements.
We report the first measurements  for $\leq$70\,MeV protons  of the  \ce{^{nat}Fe}(p,x)\ce{^{49}Cr}, \ce{^{nat}Fe}(p,x)\ce{^{51}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn},  \ce{^{nat}Fe}(p,x)\ce{^{56}Mn}, and \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} reactions, as well as the first measurement of the independent cross sections for    \ce{^{nat}Fe}(p,x)\ce{^{51}Cr}, \ce{^{nat}Fe}(p,x)\ce{^{52g}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{58g}Co}, and the \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$) and \ce{^{58\text{m}}Co} ($5^+$) / \ce{^{58\text{g}}Co}  ($2^+$)  isomer branching ratios via \ce{^{nat}Fe}(p,x).
% We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
We also use these measurements to illustrate the deficiencies in the current state of  reaction modeling up to 55\,MeV for  \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and  \ce{^{nat}Ti}(p,x) reactions.
This work offers a clear warning against unchecked use of  such default calculations, even if performed with the latest developments in nuclear reaction modeling codes. 
For work requiring even modest accuracy (say 20\%) in their default predictive capabilities, these codes clearly cannot be used to satisfaction.   
Finally, this work provides another example of the current issues with modeling of  stopping power in stacked target charged particle irradiation experiments, corrected using variance minimization techniques.  
% usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.

Notably, this work is the most well-characterized measurement of the \ce{^{nat}Fe}(p,x)\ce{^{51,52}Mn} reactions below 70\,MeV to date, with cross sections measured  at the 6--10\% uncertainty level.
This is important, as it presents the first measurement of the \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} reaction,  the first measurement of the independent \ce{^{nat}Fe}(p,x)\ce{^{52m,52g}Mn} cross sections, and extends the \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} excitation function down to the lowest energy to date.

Clearly, the use of \ce{Fe}(p,x)\ce{^{51,52}Mn} has significant untapped potential, and additional work is needed to further characterize these reaction channels for $E_p \leq$60\,MeV.

>>>>

These results have several notable features.
The 
% various 
\ce{^{nat}Fe}, \ce{^{nat}Cu}, and \ce{^{nat}Ti}(p,x) cross sections measured here are in excellent agreement with 
% the body of measurements in the 
literature,  but have been measured nearly exclusively with the highest precision to date.
While (p,x) reactions below 70\,MeV on these elements are well-characterized overall, measurements of several reaction channels are somewhat sparse in comparison.
Indeed, fewer than four existing measurements have been performed for the \ce{^{nat}Fe}(p,x)\ce{^{48}Cr},\ce{^{52}Fe}, \ce{^{nat}Cu}(p,x)\ce{^{60}Cu},\ce{^{61}Co}, and \ce{^{nat}Ti}(p,x)\ce{^{44}Sc}
% Similarly, the various \ce{^{nat}Nb}(p,x) cross sections measured here are in excellent agreement with literature data, which is far more sparse in the 40--90\,MeV region than for \ce{^{nat}Cu}(p,x) ---  fewer than three existing measurements have been performed for the majority of the 
reactions presented here.
% Indeed,  the \ce{^{nat}Nb}(p,x)\ce{^{83}Sr}, \ce{^{nat}Nb}(p,x)\ce{^{85}Y}, \ce{^{nat}Nb}(p,x)\ce{^{89}Nb}, \ce{^{nat}Nb}(p,x)\ce{^{90}Mo}, \ce{^{nat}Nb}(p,x)\ce{^{91m}Nb}, and \ce{^{nat}Nb}(p,x)\ce{^{98m}Mo} reactions each possess no more than a total of three data points in this energy region.
% Not only do the \ce{^{nat}Nb}(p,x) measurements in this work fill in the sparse data in this energy region, but they have been measured with the highest precision relative to existing literature data.
Additionally, \ce{^{22,24}Na} activity is seen in all foils, consistent with proton activation of the trace  silicon in the Kapton tape used for foil encapsulation, as described in our previous work\,\cite{Voyles2018a}.
No cross sections for \ce{^{nat}Si}(p,x)\ce{^{22,24}Na} are reported due to the significant uncertainty in characterizing the layer of silicone adhesive, but this serves as another example of how the use of silicone-based adhesives may systematically enhance the apparent fluence when using the \ce{^{nat}Al}(p,x)\ce{^{22,24}Na} monitor reactions.
Discussion of notable reaction channels follows here, and 
comparisons  of the
remaining measured cross sections 
% and isomer branching ratios 
with modeling results and literature data (retrieved from EXFOR\,\cite{Otuka2014272}) are seen in the figures of 
% Appendices 
\ref{sec:fe_xs_figures}.
% and \ref{sec:fe_ibr_figures}.

@@

        \subfigimg[width=0.485\textwidth]{\hspace{4.5cm}b)}{./figures/52Mn_IBR.pdf}{50}
         %         \refstepcounter{subfigure}
         \label{fig:temp_52mMn}
   \hspace{-5pt}}%
    \caption{a) Measured \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} cross section, with \ce{^{56}Fe}(p,$\alpha$n)\ce{^{52}Mn}/\ce{^{54}Fe}(p,2pn)\ce{^{52}Mn} reaction channels visibly peaking at approximately \mbox{30 MeV}.   b) Measured  \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$)  isomer branching ratios via \ce{^{nat}Fe}(p,x).} 
     \label{fig:discussion_52Mn}
\end{figure*}

Measured \ce{^{58\text{m}}Co} ($5^+$) / \ce{^{58\text{g}}Co}  ($2^+$)  isomer branching ratios via \ce{^{nat}Fe}(p,x), with the \ce{^{58}Fe}(p,n)\ce{^{58m}Co} reaction channel visibly peaking at approximately \mbox{20 MeV}.

@@

\subsection{\ce{^{nat}Cu}(p,x)\ce{^{60,61,64}Cu} cross sections}

\begin{figure}[h]
 \centering
 \includegraphics[width=0.5\textwidth]{./figures/64Cu.pdf}
 % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
 \caption{Measured \ce{^{nat}Cu}(p,x)\ce{^{64}Cu} independent cross section, with the \ce{^{65}Cu}(p,pn)\ce{^{64}Cu} reaction channels visibly peaking at approximately \mbox{25 MeV}.}
 \label{fig:64Cu}
\end{figure}

As with many \ce{^{nat}Cu}(p,x) channels, these reactions have been previously measured in our earlier work, but this measurement extends these cross sections down to reaction thresholds, and reports cross sections for many of the short-lived products unable to be observed previously, such as \ce{^{60}Cu} \cite{Voyles2018a}.
For \ce{^{nat}Cu}(p,x)\ce{^{60,61,64}Cu}, the measurements presented here are consistent with earlier work (aside from that of Williams \cite{PhysRev.162.1055}, as discussed earlier), and are generally the highest-precision measurements to date.

As we reported previously, modeling of \ce{^{nat}Cu}(p,x) reactions is poor in this energy region, despite the relative ease of only two stable target isotopes in copper.
For \ce{^{60}Cu}, all codes fail to predict the magnitude and shape of the channel, and tend to place the peak approximately 5\,MeV lower than observed.
Similar behavior is observed in the strongly-fed \ce{^{61}Cu}, though not to the same degree --- the peak shift is approximately 3\,MeV, but the shape predictions are more physical, despite a suppression of the pre-equilibrium tail in  EMPIRE.
\ce{^{64}Cu} modeling appears to be the best of these channels, with all codes matching the overall shape, but only EMPIRE predicting the rapid rise and fall of the compound peak, compared to the smoother behavior of the other codes.
Unlike ALICE and EMPIRE, CoH, TALYS, and TENDL all do a successful job of modeling the shape of the (p,pn) pre-equilibrium tail, with this channel showing the best predictive power of the \ce{^{nat}Cu}(p,x) reactions.
As seen with ALICE for \ce{^{61}Cu}/\ce{^{64}Cu}, the alternating underestimation/overestimation across channels for a single code points to competition between neighboring reaction channels as a common issue in this mass region.

As with the other foils in this experiment, \ce{^{nat}Cu}(p,x)  has  yielded measurements of  a number of additional  medical  radionuclides,  including the non-standard positron emitters 
\ce{^{57}Ni}\,\cite{PMID:7632762,zweit1996medium,Graves2016,Rosch2014}, 
\ce{^{61}Cu}\,\cite{Szelecsenyi2005a,Fukumura2004}, and
\ce{^{64}Cu}\,\cite{Lewis2003,Bandari2014,mp500671j,Szelecsenyi1993,Aslam2009,Hilgers2003,Szelecsenyi2005,Voyles2017}.
However, production of these radionuclides  offers no major advantages over established  pathways, with the  lower yield and radioisotopic purity failing to justify the convenience of natural targets  via    \ce{^{nat}Cu}(p,x).

\subsection{\ce{^{nat}Ti}(p,x)\ce{^{44,47,48}Sc} cross sections}

\begin{figure}[h]
 \centering
 \includegraphics[width=0.5\textwidth]{./figures/44Sc_IBR.pdf}
 % Nb_ptallies.pdf: 380x298 pixel, 72dpi, 13.41x10.51 cm, bb=0 0 380 298
 \caption{Measured \ce{^{44\text{m}}Sc} ($6^+$) / \ce{^{44\text{g}}Sc}  ($2^+$)  isomer branching ratios via \ce{^{nat}Ti}(p,x).}
 \label{fig:44Sc_IBR}
\end{figure}

Due in part to the long-standing use of Ti as a monitor foil,  \ce{^{nat}Ti}(p,x) reactions are better-characterized than many  natural targets.
While the focus of this work is on the production of \ce{^{51,52}Mn}  and other \ce{^{nat}Fe}(p,x) channels, the cross sections reported here offer improvements to prior work, particularly for the several Sc radionuclides observed. 
For all of the \ce{^{nat}Ti}(p,x)\ce{^{44,47,48}Sc} channels, this work is consistent with all prior data, and is generally the highest-precision measurement to date.
This work additionally  extends the \ce{^{44g}Sc} excitation function to the highest energy to date.

Perhaps due to the abundance of reaction data available, modeling of these channels is markedly improved  in comparison to the \ce{^{nat}Fe}(p,x) channels discussed previously.
For \ce{^{44m}Sc}, the shape of the excitation function is well-modeled by EMPIRE, CoH, TALYS, and TENDL, though all of these codes place the compound peak approximately 4\,MeV lower than observed.
Additionally, EMPIRE overestimates the magnitude of this peak, while TALYS, TENDL, and CoH significantly underestimate it.
Notably, the pre-equilibrium tail and transition towards a second peak near 65\,MeV is well-modeled by TALYS/TENDL, but signficantly underestimated by EMPIRE and CoH.
The same modeling trend is observed for \ce{^{44m}Sc}, though no judgment can be made for the pre-equilibrium tail, due to a paucity of data above 50\,MeV.
This is reflected in the measured isomer branching ratios for \ce{^{44}Sc}, seen in \autoref{fig:44Sc_IBR}.
Above 23\,MeV, TALYS/TENDL both reproduce the present work, as well as earlier measurements, suggesting that angular momentum transfer in the pre-equilibrium regime is being well-modeled, but that the total feeding of the \ce{^{44}Sc} channel is  underestimated. 
A similar argument holds for EMPIRE, which reproduces the isomer branching from threshold up to 35\,MeV.
However, CoH fails to reproduce either the channel magnitude or the isomer ratio, suggesting a more fundamental issue with the modeling of this channel. 
\ce{^{47}Sc} presents a very opposed situation, despite an abundance of reaction data and strong feeding of the channel.
All codes fail to reproduce either the shape or magnitude of this channel, with only CoH able to predict the compound peak,  and failing to model the pre-equilibrium tail.
As a cumulative reaction channel, it is unclear whether this failure arises from modeling of any \ce{^{47}Ca} decay precursors, or the competition between  \ce{^{48}Ti}(p,20)\ce{^{47}Sc} / \ce{^{49}Ti}(p,2pn)\ce{^{47}Sc} / \ce{^{50}Ti}(p,$\alpha$)\ce{^{47}Sc} channels. 
Modeling of \ce{^{48}Sc} is lacking, with only TALYS/TENDL matching the shape of the excitation, and all codes failing to reproduce the magnitude of the channel.

As with \ce{^{58m}Co} measurements, the titanium activation has  yielded measurements of  a number of additional  medical  radionuclides,  including the non-standard positron emitter
\ce{^{44}Sc}\,\cite{Muller2013,Filosofov2010,Qaim2011}
%\,\cite{Qaim2011,Qaim201731,Kolsky1998,mausner1995evaluation}.
% \ce{^{86}Y}\,\cite{Valdovinos2017,Nickles2003,Qaim2008,QaimSyedM2011,Rosch1993,doi:10.1139/v67-193,levkovski1991cross,Johnson2015,Singh2013,Kiselev1974,Kandil2009}, 
% \ce{^{89}Zr}\,\cite{Verel2003,Dijkers2009,Dijkers2010,PhysRevC.38.1624,Omara2009},  
% \ce{^{90}Nb}\,\cite{Busse2002,Radchenko2012},  
% the $\beta^-$-therapy agent  \ce{^{64}Cu},  
and the $\beta^-$-therapeutic agent 
\ce{^{47}Sc}\,\cite{Muller2014,Deilami-nezhad2016}.
% and the Auger-therapy agent \ce{^{82\text{m}}Rb}\,\cite{Kovacs1991,Titarenko2011}. 
Production of \ce{^{44}Sc} offers no major advantages over established \ce{^{44}Ca}(p,n) / \ce{^{44}Ca}(d,2n) / \ce{^{45}Sc}(p,2n)\ce{^{44}Ti} $\xrightarrow[]{\epsilon}$ \ce{^{44}Sc} pathways, with the  lower yield and radioisotopic purity failing to justify the convenience of natural targets  via    \ce{^{nat}Ti}(p,x). 
Since high-specific activity \ce{^{47}Sc} production routes are limited (with  \ce{^{47}Ti}(n,p)\ce{^{47}Sc} as one of few potential candidates), alternative pathways are greatly desired by the community.
However, \ce{^{nat}Ti}(p,x) is clearly no compelling alternative if high specific activity is required, due to the inability to avoid co-production of long-lived Sc radiocontaminants, even with prudent selection of a beam energy window.
% The one possible exception to this trend is the non-standard positron emitter \ce{^{57}Ni} ($t_{1/2}=35.60\pm0.06$ h, $\epsilon$=100\% to \ce{^{57}Co}\,\cite{Bhat1998}) --- the \ce{^{57}Ni}/\ce{^{56}Ni} ratio of production rates is approximately 290 at 61.58\,MeV, and varies from 45--75 at the 70--90\,MeV positions.
% This \ce{^{nat}Cu}(p,x) route offers both higher yield and higher radioisotopic purity over the established  \ce{^{nat}Co}(p,3n) pathway, which suffers from approximately fivefold greater  \ce{^{56}Ni} contamination\,\cite{MICHEL1997153,Ditrói2013}.
% The one potential exception to this is the production of \ce{^{58m}Co}, a potent agent for Auger electron-based targeted therapy\,\cite{Thisgaard2011a,Valdovinos2017b,Thisgaard2014a}.
% While ingrowth of the long-lived \ce{^{58g}Co} ($t_{1/2}$ = 70.86(6) d\,\cite{Nesaraja2010}) is unavoidable, minimizing co-production of \ce{^{58g}Co} is necessary to minimize patient dose.
% The \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} pathway shows a clear \enquote{peak} in the \ce{^{58m}Co}/\ce{^{58g}Co} branching ratio for approximately 15--30\,MeV protons, which might have translational implications if Auger electron therapy becomes more clinically prevalent.

@@

We present here a set of measurements of 34 cross sections for the \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and  \ce{^{nat}Ti}(p,x) reactions up to 55\,MeV, as well as  independent measurements of three isomer branching ratios.
Nearly all cross sections have been reported with higher precision than previous measurements.
We report the first measurements  for $\leq$70\,MeV protons  of the  \ce{^{nat}Fe}(p,x)\ce{^{49}Cr}, \ce{^{nat}Fe}(p,x)\ce{^{51}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{52m}Mn},  \ce{^{nat}Fe}(p,x)\ce{^{56}Mn}, and \ce{^{nat}Fe}(p,x)\ce{^{58m}Co} reactions, as well as the first measurement of the independent cross sections for    \ce{^{nat}Fe}(p,x)\ce{^{51}Cr}, \ce{^{nat}Fe}(p,x)\ce{^{52g}Mn}, \ce{^{nat}Fe}(p,x)\ce{^{58g}Co}, and the \ce{^{52\text{m}}Mn} ($2^+$) / \ce{^{52\text{g}}Mn}  ($6^+$) and \ce{^{58\text{m}}Co} ($5^+$) / \ce{^{58\text{g}}Co}  ($2^+$)  isomer branching ratios via \ce{^{nat}Fe}(p,x).
Clearly, the use of \ce{Fe}(p,x)\ce{^{51,52}Mn} has significant untapped potential, and additional work is needed to further characterize these reaction channels for $E_p \leq$60\,MeV, as well as the potential for \ce{^{nat}Fe}(p,x)\ce{^{54}Mn},\ce{^{56}Co} as future monitor reactions.
% We advise that future activation experiments avoid the use of silicone-based adhesives, particularly in conjunction with aluminum monitor foils, to avoid reporting an enhanced fluence due to \ce{^{22,24}Na} contamination.
We also use these measurements to illustrate the deficiencies in the current state of  reaction modeling up to 55\,MeV for  \ce{^{nat}Fe}(p,x), \ce{^{nat}Cu}(p,x), and  \ce{^{nat}Ti}(p,x) reactions.
This work offers a clear warning against unchecked use of  such default calculations, even if performed with the latest developments in nuclear reaction modeling codes. 
For work requiring even modest accuracy (say 20\%) in their default predictive capabilities, these codes clearly cannot be used to satisfaction.   
Finally, this work provides another example of the current issues with modeling of  stopping power in stacked target charged particle irradiation experiments, corrected using variance minimization techniques.  
% usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.
% 
% Notably, this work is the most well-characterized measurement of the \ce{^{nat}Fe}(p,x)\ce{^{51,52}Mn} reactions below 70\,MeV to date, with cross sections measured  at the 6--10\% uncertainty level.
% This is important, as it presents the first measurement of the \ce{^{nat}Fe}(p,x)\ce{^{51}Mn} reaction,  the first measurement of the independent \ce{^{nat}Fe}(p,x)\ce{^{52m,52g}Mn} cross sections, and extends the \ce{^{nat}Fe}(p,x)\ce{^{52}Mn} excitation function down to the lowest energy to date. 
%
